---
title: "HW13"
author: "許循閒"
date: "2019年5月27日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##checkpoint_3_forcats
```{r}
library(tidyverse)
library(tidyquant)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")
bike_orderlines_tbl
```
#讀取資料
執行tidyverse、tidyquant

用read_rds 讀取bike_orderlines.rds 資料

```{r}
sales_by_cat_2_tbl <- bike_orderlines_tbl %>%
    select(category_2, total_price) %>%
    group_by(category_2) %>%
    summarize(sales = sum(total_price)) %>%
    ungroup() %>%
    arrange(desc(sales)) %>%
    mutate(category_2 = category_2 %>% as_factor() %>% fct_rev())
```

# Manipulation
用select函數選擇需要的欄位

用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

用arrange函數將資料排列整理

desc函數 - 由大到小排列

fct_rev() - 反轉資料

```{r}
sales_by_cat_2_tbl %>%
    ggplot(aes(x = sales, y = category_2)) +
    geom_point(size = 5, color = "#2c3e50") +
    labs(title = "Sales By Category 2") +
    scale_x_continuous(labels = scales::dollar_format()) +
    theme_tq() +
    expand_limits(x = 0)

plot_sales <- function(data) {
    data %>%
        ggplot(aes(x = sales, y = category_2)) +
        geom_point(size = 5, color = "#2c3e50") +
        labs(title = "Sales By Category 2") +
        scale_x_continuous(labels = scales::dollar_format()) +
        theme_tq() +
        expand_limits(x = 0)
}

sales_by_cat_2_tbl %>%
    plot_sales()
```

# Plotting
用geom_point函數畫點

theme_tq() - 美化圖表

plot_sales <- function(data) - 設定函數方便使用

```{r}
sales_by_cat_2_tbl %>% pull(category_2) %>% levels()
sales_by_cat_2_tbl %>% pull(category_2) %>% as.numeric()
```

# Vector
pull函數 - 將資料拉出

as.numeric() - 數字形式

```{r}
sales_by_cat_2_tbl %>%
    mutate(category_2 = category_2 %>% fct_rev() %>% fct_rev()) %>%
    mutate(
        label = category_2 %>% as.character(),
        value = category_2 %>% as.numeric()
    )
```

# Tibble
用mutate函數新增新的欄位資料

label為文字形式

value為數字形式

```{r}
sales_by_cat_2_tbl %>%
    mutate(
        category_2           = as.character(category_2),
        category_2_as_factor = as_factor(category_2) %>% as.numeric(),
        category_2_as.factor = as.factor(category_2) %>% as.numeric()
    )
```

# Creating Factors: as_factor() vs as.factor()
用mutate函數新增新的欄位資料

category_2為文字形式

category_2_as_factor、category_2_as.factor為數字形式

as_factor - 以原本的排列作排列
 
as.factor - 以英文字母排列

```{r}
sales_by_cat_2_tbl %>%
    arrange(desc(sales)) %>%
    mutate(sales_negative = -sales) %>%
    mutate(
        category_2 = category_2 %>% fct_reorder(sales_negative),
        values     = category_2 %>% as.numeric()) %>%
    plot_sales()
```

# Reordering Factors: fct_reorder() and fct_rev()
用arrange函數將資料排列整理

desc函數 - 由大到小排列

用mutate函數新增新的欄位資料

fct_reorder函數 - 針對因子排序

category_2為文字形式

```{r}
sales_by_cat_2_q_tbl <- bike_orderlines_tbl %>%
    mutate(order_date = order_date %>% floor_date("quarter") %>% ymd()) %>%
    group_by(category_2, order_date) %>%
    summarise(sales = sum(total_price)) %>%
    ungroup()

sales_by_cat_2_q_tbl


sales_by_cat_2_q_tbl %>%
    mutate(category_2 = category_2 %>% fct_reorder2(order_date, sales)) %>%
    ggplot(aes(x = order_date, y = sales, color = category_2)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ category_2) +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M"))
```

# Time-Based Reordering: fct_reorder2()
用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

用geom_point函數畫點

用geom_line函數畫線

facet_wrap函數 - 打資料分成很多小圖

theme_tq() 、scale_color_tq()美化圖表

```{r}
sales_by_cat_2_tbl %>%
    mutate(category_2 = category_2 %>% fct_lump(n = 6, 
                                                w = sales, 
                                                other_level = "All Other Bike Categories")) %>%
    group_by(category_2) %>%
    summarize(sales = sum(sales)) %>%
    mutate(category_2 = category_2 %>% fct_relevel("All Other Bike Categories", after = 0)) %>%
    plot_sales()
```

# Creating "Other" Category - fct_lump() & fct_relevel()
用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

fct_lump函數 - 把資料堆疊

fct_relevel函數 - 把資料重新排序





##02_ggplot_geometries_1
```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)

bike_orderlines_tbl <- read_rds("data_wrangled_student/bike_orderlines.rds")
glimpse(bike_orderlines_tbl)
```
#讀取資料
執行tidyverse、tidyquant、lubridate

用read_rds 讀取bike_orderlines.rds 資料

```{r}
order_value_tbl <- bike_orderlines_tbl %>%
    select(order_id, order_line, total_price, quantity) %>%
    group_by(order_id) %>%
    summarize(
        total_quantity = sum(quantity),
        total_price    = sum(total_price)
    ) %>%
    ungroup()
```

# Data Manipulation(Explain relationship between order value and quantity of bikes sold)
用select函數選擇需要的欄位

用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

```{r}
order_value_tbl %>%
    ggplot(aes(x = total_quantity, y = total_price)) +
    geom_point(alpha = 0.5, size = 2) +
    geom_smooth(method = "lm", se = FALSE)
```

# Scatter Plot(Explain relationship between order value and quantity of bikes sold)
用aes設定X與Y軸

用geom_point函數畫點

alpha - 透明度

geom_smooth函數畫平滑線(lm - 回歸)

```{r}
revenue_by_month_tbl <- bike_orderlines_tbl %>%
    select(order_date, total_price) %>%
    mutate(year_month = floor_date(order_date, "months") %>% ymd()) %>%
    group_by(year_month) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```

# Data Manipulation(Describe revenue by Month, expose cyclic nature)
用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

floor_date函數 - 取第一天的資料

```{r}
revenue_by_month_tbl %>%
    ggplot(aes(year_month, revenue)) +
    geom_line(size = 0.5, linetype = 1) +
    geom_smooth(method = "loess", span = 0.2)
```

# Line Plot(Describe revenue by Month, expose cyclic nature)
用aes設定X與Y軸

用geom_linet函數畫線

geom_smooth函數畫平滑線(loess - 曲線)

```{r}
revenue_by_category_2_tbl <- bike_orderlines_tbl %>%
    select(category_2, total_price) %>%
    group_by(category_2) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```

# Data Manipulation(Sales by Descriptive Category)
用select函數選擇需要的欄位

用summarize函數總整所有資料

用group_by函數 - 群組起來

```{r}
revenue_by_category_2_tbl %>%
    mutate(category_2 = category_2 %>% as_factor() %>% fct_reorder(revenue)) %>%
    ggplot(aes(category_2, revenue)) +
    geom_col(fill = "#2c3e50") + 
    coord_flip()
```

# Bar Plot(Sales by Descriptive Category)
用mutate函數新增新的欄位資料

geom_col函數畫欄

coord_flip()函數 - X與Y軸對調

```{r}
bike_orderlines_tbl %>%
    distinct(price, model, frame_material) %>%
    ggplot(aes(price, fill = frame_material)) +
    geom_histogram() +
    facet_wrap(~ frame_material, ncol = 1) +
    scale_fill_tq() +
    theme_tq()
```

# Histogram(Unit price of bicylce, segmenting by frame material)
distinct函數 - 把重複資料刪除取唯一一個

用aes設定X與Y軸

geom_histogram()畫直方圖

scale_fill_tq()、theme_tq() - 用來美化圖表

facet_wrap函數 - 打資料分成很多小圖

```{r}
bike_orderlines_tbl %>%
    distinct(price, model, frame_material) %>%
    ggplot(aes(price, fill = frame_material)) +
    geom_density(alpha = 0.5) +
    # facet_wrap(~ frame_material, ncol = 1) +
    scale_fill_tq() +
    theme_tq() +
    theme(legend.position = "bottom")
```

# Density(Unit price of bicylce, segmenting by frame material)
distinct函數 - 把重複資料刪除取唯一一個

用aes設定X與Y軸

geom_density畫曲線分布圖

scale_fill_tq()、theme_tq() - 用來美化圖表

```{r}
unit_price_by_cat_2_tbl <- bike_orderlines_tbl %>%
    select(category_2, model, price) %>%
    distinct() %>%
    mutate(category_2 = as_factor(category_2) %>% fct_reorder(price))
```

# Data Manipulation(Unit price of model, segmenting by category 2)
distinct函數 - 把重複資料刪除取唯一一個

用select函數選擇需要的欄位

用mutate函數新增新的欄位資料

```{r}
unit_price_by_cat_2_tbl %>%
    ggplot(aes(category_2, price)) +
    geom_boxplot() +
    coord_flip() +
    theme_tq()
```

# Box Plot(Unit price of model, segmenting by category 2)
用aes設定X與Y軸

geom_boxplot畫盒狀圖

coord_flip()函數 - X與Y軸對調

theme_tq()美化圖表

```{r}
unit_price_by_cat_2_tbl %>%
    ggplot(aes(category_2, price)) +
    geom_jitter(width = 0.15, color = "#2c3e50") +
    geom_violin(alpha = 0.5) +
    coord_flip() +
    theme_tq()
```

# Violin Plot & Jitter Plot(Unit price of model, segmenting by category 2)
用aes設定X與Y軸

coord_flip()函數 - X與Y軸對調

theme_tq()美化圖表

```{r}
revenue_by_year_tbl <- bike_orderlines_tbl %>%
    select(order_date, total_price) %>%
    mutate(year = year(order_date)) %>%
    group_by(year) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()
```

# Data Manipulation(Exposing sales over time, highlighting outlier)
用select函數選擇需要的欄位

用mutate函數新增新的欄位資料

用summarize函數總整所有資料

用group_by函數 - 群組起來

```{r}
revenue_by_year_tbl %>%
    # mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>%
    ggplot(aes(year, revenue)) +
    geom_col(fill = "#2c3e50") +
    geom_smooth(method = "lm", se = FALSE) +
    geom_text(aes(label =  scales::dollar(revenue, scale = 1e-6, suffix = "M")), 
              vjust = 1.5, color = "white") +
    geom_label(label =  "Major Demand This Year",
               vjust = -0.5, 
               size  = 5,
               fill  = "#1f78b4",
               color = "white",
               fontface = "italic",
               data = revenue_by_year_tbl %>%
                   filter(year %in% c(2013))) + 
    expand_limits(y = 2e7) +
    theme_tq()
```

# Adding text to bar chart
# Filtering labels to highlight a point(Exposing sales over time, highlighting outlier)
用aes設定X與Y軸

geom_col函數畫欄

geom_smooth函數畫平滑線

用geom_text函數把文字標示在圖表上

用geom_label函數修改標籤資料

theme_tq()美化圖表





